---
title: "Example Analysis Report"
author: "Hakile Resulbegović"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(psych)
library(broom)
```

# Introduction

This report demonstrates a basic reproducible analysis workflow using synthetic data from the repository *R for Applied Psychology Students: Open Materials for Data Analysis in Psychological Research*.

The data are synthetic and are used only for teaching.

# Data import

```{r}
data <- read_csv("../data/processed/student_psychology_synthetic_scored.csv")
glimpse(data)
```

# Descriptive statistics

```{r}
describe(data %>%
           select(perceived_stress_score, digital_stress_score,
                  academic_motivation_score, wellbeing_score,
                  exam_anxiety_score))
```

# Visualization

```{r}
ggplot(data, aes(x = perceived_stress_score, y = wellbeing_score)) +
  geom_point(alpha = 0.70) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    title = "Perceived Stress and Well-being",
    x = "Perceived stress score",
    y = "Well-being score"
  )
```

# Correlation

```{r}
cor.test(data$perceived_stress_score, data$wellbeing_score)
```

# Regression

```{r}
model <- lm(wellbeing_score ~ perceived_stress_score + digital_stress_score +
              academic_motivation_score + sleep_hours,
            data = data)

summary(model)
broom::tidy(model, conf.int = TRUE)
```

# Reporting note

The results above are based on synthetic data and should not be interpreted as evidence about real students.
